\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-09 paper.qmd
Added Figure title

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "none", 
     legend.title = element_text(size=5), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
interior_annotation <- function(label) {
  annotation_custom(grid::textGrob(label = label,
      x = unit(0.92, "npc"), y = unit(0.92, "npc"),
      gp = grid::gpar(cex = 1, col="grey70")))
}
```

@@

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  interior_annotation("a")
```

@@

hex_grid_scurve <-  ggplot(data = hex_grid_with_counts, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  interior_annotation("b")
```

@@

hex_grid_nonempty_scurve <-  ggplot(data = hex_grid_nonempty, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = df_bin_centroids, aes(x = c_x, y = c_y), color = "#33a02c") +
  interior_annotation("c") 
```

@@

trimesh_removed_scurve <- vis_rmlg_mesh(distance_edges = distance_scurve, 
                                        benchmark_value = benchmark_scurve, 
                                        tr_coord_df = tr_from_to_df_scurve, 
                                        distance_col = "distance") +
  interior_annotation("d") 
```

```{r}
#| label: fig-NLDR-scurve
#| echo: false
#| fig-cap: ""
#| fig-width: 8
#| fig-height: 4
#| out-width: 100%

>>>>

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "none", 
     legend.title = element_text(size=5), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
interior_annotation <- function(label) {
  annotation_custom(grid::textGrob(label = label,
      x = unit(0.92, "npc"), y = unit(0.92, "npc"),
      gp = grid::gpar(cex = 1, col="grey70")))
}

interior_annotation_left <- function(label) {
  annotation_custom(grid::textGrob(label = label,
      x = unit(0.08, "npc"), y = unit(0.93, "npc"),
      gp = grid::gpar(cex = 1, col="grey70")))
}
```

@@

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  interior_annotation_left("a")
```

@@

hex_grid_scurve <-  ggplot(data = hex_grid_with_counts, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  interior_annotation_left("b")
```

@@

hex_grid_nonempty_scurve <-  ggplot(data = hex_grid_nonempty, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id), fill = "#ffffff") +
  geom_point(data = df_bin_centroids, aes(x = c_x, y = c_y), color = "#33a02c") +
  interior_annotation_left("c") 
```

@@

trimesh_removed_scurve <- vis_rmlg_mesh(distance_edges = distance_scurve, 
                                        benchmark_value = benchmark_scurve, 
                                        tr_coord_df = tr_from_to_df_scurve, 
                                        distance_col = "distance") +
  interior_annotation_left("d") 
```

```{r}
#| label: fig-NLDR-scurve
#| echo: false
#| fig-cap: "Key steps for constructing the $2-D$ model for S-curve data: (a) obtain UMAP data, (b) hexagonating UMAP data, (c) obtain hexagonal bin centroids, and (d) triangulate bin centroids."
#| fig-width: 8
#| fig-height: 4
#| out-width: 100%

### 2024-04-09 paper.tex
Added UMAP layout for S-curve data
Add plots for 2D model construction
Added Figure title

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-NLDR-scurve-1.pdf}

\caption{\label{fig-NLDR-scurve}Key steps for constructing the \(2-D\)
model for S-curve data: (a) obtain UMAP data, (b) hexagonating UMAP
data, (c) obtain hexagonal bin centroids, and (d) triangulate bin
centroids.}
